Simulation

### 2024-06-25 Simulation1.Rmd
Martes tarde

```{r}
list <- list_stable
for (l in 1:599) {
  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
    a <- runif(1, vec[k + (nb-1)*60], vec[k + (nb-1)*60] + 1)
    b <- runif(1, 200 + (l-1), 200+l)
    random_points <- rbind(random_points, list(a,b))
    # trees$cell <- ifelse(
    # (vec[] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
    # list_stable[nb],
    # trees$cell)
  }
  list <- shift(list, n = trend, type = "cyclic") # shift for each line
}

@@

```{r}
plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
# Semble régulier si nb = 2
```

```{r}
plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(202, 205), ylim = c(200, 205))
# Un seul point par cellule
```

@@

```{r}
# Adding columns to the dataframe
# Number of trees inside each circle around each random point ; Total of diameter ; Total volume
for (point in 1:36000) {
  trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
  # x, y, h, k, R
  total_trees <- nrow(trees[trees$Is_in_circle == TRUE,])
  total_d130 <- sum(trees[trees$Is_in_circle == TRUE,]$d130)
}
random_points
```

>>>>

```{r}
# Wrong algorithm
list <- list_stable
for (l in 1:599) {
  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
    a <- runif(1, vec[k + (nb-1)*60], vec[k + (nb-1)*60] + 1)
    b <- runif(1, 200 + (l-1), 200+l)
    random_points <- rbind(random_points, list(a,b))
    # trees$cell <- ifelse(
    # (vec[] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
    # list_stable[nb],
    # trees$cell)
  }
  list <- shift(list, n = trend, type = "cyclic") # shift for each line
}

@@

```{r}
plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
# Semble régulier si nb = 2, idem si nb = 8
```

```{r}
plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(202, 205), ylim = c(205, 210))
# Un seul point par cellule
```

@@

```{r}
# Adding columns to the dataframe
# Number of trees inside each circle around each random point ; Total of diameter ; Total volume
for (point in 1:36000) {
  trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
  # x, y, h, k, R
  total_trees <- nrow(trees[trees$Is_in_circle == TRUE,])
  total_d130 <- sum(trees[trees$Is_in_circle == TRUE,]$d130)
}
# random_points
```
